
% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{format}
\usepackage{xcolor}
\usepackage[allbordercolors=white]{hyperref}
% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Lohitaksh Trehan}
\address{\#218, Ram Nagar, Ambala City\linebreak Haryana, ZIP-134003}
\contacts{(+91)-8053602204 \linebreak \href{mailto:lohitakshtrehan@gmail.com}{lohitakshtrehan@gmail.com}}

\begin{document}

	% Print the header
	\makeheader
	\vspace{-3pt}
	% Print the content
	\begin{cvsection}{Employment}
	
	    \vspace{2pt}
	
	    \begin{cvsubsection}{Product Engineer}{Sprinklr India Pvt. Ltd.}{Dec, 2020 – Present}
			\textit{Modern Care Product}
			\begin{itemize}
				\item Currently working as a Product Engineer for the Modern-Care product using which brands can proactively listen to customers across multiple channels, automatically route inbound messages to the right agent, quickly resolve customer issues using their full history and analyze the overall performance of the care program in order to make improvements.
				\item Actively working with frontend technologies like ReactJS, GraphQL, SASS etc to build the product.
			\end{itemize}
		\end{cvsubsection}
	
		\begin{cvsubsection}{Software Developer}{ION Trading India Pvt. Ltd.}{Jun, 2019 – Nov, 2020}
			\textit{ION Core Architecture Web Stack}
			\begin{itemize}
				\item In a global scrum team of 12 people, we shaped, developed and provided standards for web development. Which are then implemented by other internal teams for all the web-based products of the organization.
				\item During my tenure, I developed features using AngularJS as the core technology stack and owned various components of the SDK.
				\item Worked on migration of the product to add support of web-components. This made our product accessible to teams which were not using AngularJS, increasing product adoption rate by 30\%.
				\item Contribution in other roles for the product like designing UX, managing client requests and building UI automation tests was also part of the job.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Developer, Intern}{Tata Consultancy Services}{Jun, 2018 – Jul, 2018}
		    \textit{UI Controlled Test Automation Framework}
			\begin{itemize}
				\item In a team of 3, we designed and implemented a framework from scratch to automate testing of Wireless Access Points.
				\item In a duration of 2 months, I created the graphical user interface using Angular-4 for the user to troubleshoot and log any problems discovered during the run of automated tests.
				\item Also Developed some of the required API’s in Django for handling the troubleshooting actions triggered by the user.
				\item Responsibilities also included preparing power points of the product and giving demo of the product to the client. The project was delivered on time and contributed 80\% of time reduction for the client to test their Wifi Access Points
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Full Stack Developer, Intern}{HeadStartr}{Jan, 2018 – Feb, 2018}		
			\begin{itemize}
				\item Coordinated a team of 4, as a project leader during the remote internship.
				\item Implemented OAuth strategies using MERN stack, which are then used by the application for a secure login system.
			\end{itemize}
		\end{cvsubsection}
		
	\end{cvsection}
	
	\vspace{-5pt}
	
	\begin{cvsection}{Education}
	
	    \vspace{2pt}
	
		\begin{tabu} to 1\textwidth { X[l,p] X[c,p] X[r,p] }
			\textbf{Institute} & \textbf{Degree/Exam} & \textbf{GPA/Percentage – (Year)} \\
			Indian Institute of Info. Tech. Sonepat & B.Tech [Computer-Science] & 8.5211/10 – (2019) \\
			Murlidhar DAV Public School & CBSE - XII & 90.2\% – (2015) \\
			Murlidhar DAV Public School & CBSE - X & 95\% – (2013)
		\end{tabu}
		
	\end{cvsection}

	\vspace{-5pt}

	\begin{cvsection}{Technical Skills}
	\vspace{-6pt}
	\hspace{1.925pt}
		\begin{tabu} to 1\textwidth { X[l,p] X[l,p] X[0.7l,p] }
			\begin{itemize}
			    \item ReactJS, GraphQL, AngularJS, Web Components
			    \item Integration Testing Using Selenium and Robot Framework
			\end{itemize} & \begin{itemize}
			    \item HTML, CSS, Javascript, TypeScript, LESS, SASS
			    \item Functional Programming and Object Oriented Programming
			\end{itemize} & \begin{itemize}
			    \item Data Structures and Software Design Patterns
			    \item NPM, NodeJS, MongoDB, Basic Bash scripting
			\end{itemize}
		\end{tabu}
	\end{cvsection}
	
	\vspace{-20pt}
	
	\begin{cvsection}{Scholastic Distinctions}
	\vspace{2pt}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Awarded certificate of excellence by CBSE for being in top 0.1 percentile in Mathematics.
                \item Selected for ACM-ICPC 2018 India Level Qualifier, with Amritapuri site rank of 178 and rank 1 in college.
                \item Achieved rank of 1005 in Facebook Hacker Cup 2018 (round-2).
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\vspace{-5pt}
	
	\begin{cvsection}{Professional Profiles}
	    \vspace{2pt}
	    \begin{cvsubsection}{}{}{}
	    \textbullet\ \small{\url{https://www.linkedin.com/in/lohitaksh-trehan-013117108/}} \hfill \textbullet\ \small{\url{https://github.com/LohitakshTrehan}}
	    \end{cvsubsection}
	\end{cvsection}
	
\end{document}
